Numerical Stability of Detonations in White Dwarf Simulations

### 2019-02-05 papers/ignition/paper.tex
add facility keyword
Abstract

%==========================================================================
% Abstract
%==========================================================================
\begin{abstract}
Some simulations of Type Ia supernovae feature thermonuclear detonations that
arise self-consistently during the evolution. It is not clear whether these
detonations would occur in a simulation that fully resolved the burning. In this
study we examine a test detonation problem inspired by collisions of white dwarfs.
This test problem demonstrates that achieving a converged thermonuclear ignition
requires spatial resolution much finer than 1 km in the burning region, and that
the simulation as a whole likely needs a base resolution on the order of 1 km or better.
Current computational resource constraints place this stringent resolution requirement
out of reach for almost all multi-dimensional supernova simulations.
Consequently, contemporary simulations that self-consistently demonstrate
detonations are very likely not resolved and should be treated with caution.
\end{abstract}
\keywords{supernovae: general - white dwarfs}

@@

>>>>

%==========================================================================
% Abstract
%==========================================================================
\begin{abstract}
Some simulations of Type Ia supernovae feature self-consistent thermonuclear
detonations. However, these detonations are not meaningful if the simulations
are not resolved, so it is important to establish an understanding of the
requirements for achieving a numerically converged detonation. In this
study we examine a test detonation problem inspired by collisions of white dwarfs.
This test problem demonstrates that achieving a converged thermonuclear ignition
requires spatial resolution much finer than 1 km in the burning region.
Current computational resource constraints place this stringent resolution
requirement out of reach for multi-dimensional supernova simulations.
Consequently, contemporary simulations that self-consistently demonstrate
detonations are very likely not resolved and should be treated with caution.
\end{abstract}
\keywords{supernovae: general - white dwarfs}

@@

\facility{OLCF}
